Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
still revising bandpass correction discussion

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
therefore computed dimensionless bandpass correction factors:

\begin{equation}
b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

@@

% also need to define what \mathcal{T} is (planck transmission, 
% dimensionless)

The two-component model prediction in band $\nu_i$ is then constructed
as a linear combination of color-corrected MBB terms:

@@

Note that by convention $f_2$=(1$-$$f_1$)

%pre-computing lookup tables of b_{\nu_i} allows us to evaluate the 
% relevant modified blackbodies at the nominal  band center frequency 
% and then obtain the broadband measurement by virtue of multiplying by
% by the relevant b_{\nu_i}

Is the predicted observation for the \PLANCK~or \IRAS~band of interest. Here 
$\nu_i$ represents the $i^{th}$ of the five nominal band center frequencies for
which we have broadband measurements, $\nu_i \in$ \{217, 353, 545, 857, 3000\} 
GHz. We have used the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
the DIRBE bandpass.

>>>>

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density $M_{\nu}$ in e.g. MJy/sr for any single frequency $\nu$. In 
practice, however, we wish to constrain our model using measurements in the 
broad \verb|i100|/\PLANCK~bandpasses, typically hundreds of GHz wide. We have 
therefore computed dimensionless finite bandpass correction factors to 
account for the MBB($\beta$, $T$) spectral shape and the transmission as a 
function of frequency:

\begin{equation}
b_{\nu_i}(T, \beta) = \frac{\int \mathcal{T}_{\nu_i}(\nu)\nu^{\beta}B_{\nu}(T) d\nu \bigg[\int \mathcal{T}_{\nu_i}(\nu) d\nu\bigg]^{-1}}{\nu_{i,c}^{\beta}B_{\nu_{i,c}}(T)}
\end{equation}

% integral limits ??? check planck paper to see what they did

@@

% also need to define what \mathcal{T} is (relative transmission, 
% dimensionless)

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 3000\} GHz. 
$\mathcal{T}_{\nu_i}(\nu)$ represents the relative transmission as a function 
of frequency for band $\nu_i$. For the HFI maps, $\mathcal{T}_{\nu_i}(\nu)$ is 
given by the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
adopted the DIRBE bandpass.

The broadband, two-component model prediction in band $\nu_i$, termed 
$\tilde{I}_{\nu_i}$,is then constructed as a linear combination of 
color-corrected MBB terms:

@@

Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. This finite bandpass 
correction approach allows us to predict the \textit{broadband} measurement 
$\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the central 
frequency $\nu_{i,c}$ and then multiplying by factors $b_{\nu_i}(T, \beta)$ 
which are interpolated off of a set of precomputed, one-dimensional lookup 
tables. Here the single dimension is $T_k$, as we avoid the necessity of a 
two-dimensional interpolation in both $\beta$ and $T$ by computing a small set 
of one dimensional correction factors for the particular set of $\beta$ values
of interest ($\beta$$\in$\{1.67, 2.7, 1.19, 2.61\}, see Table \ref{tab:global}.

% maybe a final sentence to emphasize explicitly that this approach
% is much more computationally feasible than computing integrals
% on-the-fly every time a putative model is proposed (during sampling)

% maybe mention the motivation for computing b_{\nu_i} on a **per MBB**
% basis, the fact that this is more versatile, especially when 
% the ``global parameters'' like f_1 or others are being changed
